Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
swap completeness and sampling checks in fig 2

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Completeness Threshold} (aux1);

>>>>

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Complete}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Sampling}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Completeness\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Completeness Threshold} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Sampling Rate} (aux1);
